\documentclass[a4paper]{article}
    \usepackage[T1]{fontenc}
    \usepackage[sfdefault]{biolinum}   %% Option 'sfdefault' only if
    \usepackage[utf8]{inputenc}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{fullpage}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {John Y. Rodgers}}\\
	San Diego, CA $\cdot$ jyrodgers@protonmail.com $\cdot$ Github/LinkedIn: @jyrodgers $\cdot$ 858-231-4371 \\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Viasat} \hfill San Diego, CA\\
\textit{Software Engineer} \hfill August 2018 - November 2023\\
\vspace{-1mm}
\begin{itemize}
	\item Designed and owned \textbf{C++} library for managing \textbf{OpenSSL}-secured \textbf{DTLS} connections, including client/server roles and \textbf{multi-threading} for heartbeat monitoring and packet queuing.
	\item Cut application suite build/test time by over 3 hours by initiating and guiding an intern project. Implemented contemporary \textbf{CMake} and \textbf{Docker} image patterns and upgraded build tools for efficiency.
	\item Streamlined project workflows, managed tasks in \textbf{JIRA}, facilitated meetings, and collaborated with leaders across teams to drive successful project outcomes.
	\item Developed multi-client to server publishing microservice that streamed monitoring/analysis data from \textbf{Docker}/\textbf{Kubernetes} containers. Integrated \textbf{gRPC}, \textbf{Fluent Bit}, \textbf{Kafka}, \textbf{Grafana}, and \textbf{Splunk}.
	\item Revitalized code review processes, empowering developers of all skills to actively contribute/learn from every PR, reducing time to merge, integrated \textbf{GitHub} tools to streamline review process.
	\item Owned library for recovering "black box" log files from failed \textbf{Docker}/\textbf{Kubernetes} containers, leveraging multiple \textbf{threads}, \textbf{circular buffers}, \textbf{IPC}-based communication, and remote \textbf{volume store}.
	\item \textbf{Deployed}, debugged and administered \textbf{Linux-based VMs} using \textbf{Jenkins} to develop, test, and deploy \textbf{Docker}/\textbf{Kubernetes} containers.
	\item Ensured rapid issue resolution and system reliability through critical \textbf{on-call technical support}, demonstrating a deep understanding of system architecture and cross-team product integration.
	\item Streamlined artifact synchronization between legacy Perforce and host build system using Docker/Kubernetes container. Implemented Bash scripting and volume mounts for efficient file transfer.
	\item Lowered dependency on individual expertise by initiating peer education program, conducting needs assessments, mobilizing subject matter experts, and creating a comprehensive video knowledge base.
	\item Boosted technical proficiency by starting junior developer skill-up sessions resulting in a knowledge base of \textbf{Zettelkasten} and \textbf{Diátaxis} based notes populated with \textbf{C4}, \textbf{Sequence}, and \textbf{State} Diagrams.
	\item Eliminated \textbf{cybersecurity} risks by monitoring vulnerabilitites using \textbf{Blackduck} and \textbf{Security Scorecard}, JIRA tracking of resolution, leading to a perfect security assessment for the project.
	\item Mastered complex \textbf{regular expressions} for file identification by name and content with tools such as \textbf{find}, \textbf{ripgrep}, and \textbf{ag}, applied techniques for mass text editing in \textbf{Vim} and \textbf{Obsidian}.
	\item Deep intellectual curiosity and passion about learning through \textbf{methodical study}, \textbf{organized note-taking} using Zettelkasten method, systematic reviews using \textbf{spaced repetition flashcards}.
\end{itemize}

\vspace{-1mm}
\textbf{Viasat} \hfill San Diego, CA\\
\textit{Software Engineer Intern} \hfill June 2017 - August 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Collaborated with an interdisciplinary team to consolidate multiple hardware testing tools into a single server rack, automating modem testing processes.
    \item Created equipment tests using C++, automated tests and reporting of results using \textbf{Python}, ensuring seamless communication and compatibility between devices.
    \item Performed extensive debugging and optimization of the automated system, ensuring robust performance in diverse operational conditions.
\end{itemize}

\textbf{United States Navy} \hfill \\
\textit{Information Systems Technician} \hfill 2007 - 2012\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Obtained \textbf{TS/SCI Security Clearance}, demonstrating a commitment to stringent security protocols and a proven track record of trustworthiness and reliability in handling classified information.
	\item Configured, maintained, and monitored ship-wide \textbf{local-area network} including \textbf{servers}, \textbf{firewalls}, \textbf{routers}, and \textbf{switches}.
	\item Supervised five-member team of diverse backgrounds and life experiences through daily operations by focusing on respect, communication, and motivation.
\end{itemize}

%==== Education ====%
\header{Education}
\textbf{University of California San Diego}\hfill \\
\textit{Jacobs School of Engineering} \\
BS in Computer Science \hfill \\
\begin{itemize} \itemsep 1pt
	\item Coursework: Object-Oriented Programming; Advanced Data Structures; Theory of Computability; Software Engineering; Computer Architecture; Artificial Intelligence: Search \& Reasoning; Computer Operations \& Product Engineering \\
\end{itemize}

\vspace{2mm}

\end{document}
