\documentclass[a4paper]{article}
    \usepackage[T1]{fontenc}
    \usepackage[sfdefault]{biolinum}   %% Option 'sfdefault' only if
    \usepackage[utf8]{inputenc}
    \usepackage{amsmath}
    \usepackage{hyperref}
    \usepackage{amssymb}
    \usepackage{fullpage}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {John Y. Rodgers}}\\
	jyrodgers@protonmail.com $\cdot$ \href{https://www.linkedin.com/in/jyrodgers/}{linkedin.com/in/jyrodgers} $\cdot$ \href{https://github.com/jyrodgers}{github.com/jyrodgers} $\cdot$  858-231-4371 \\
\end{center}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Viasat} \hfill San Diego, CA\\
\textit{Software Engineer} \hfill August 2018 - January 2024\\
\vspace{1mm}
\begin{itemize}
	\item Improved compliance with rigorous security standards in cross-virtual machine communications by designing and owning a \textbf{C++} library that managed \textbf{OpenSSL}-secured \textbf{DTLS} connections.
        \begin{itemize}
	        \item Prioritized developer convenience with robust API, allowing easy setup of encryption, timeout, SSL roles, and peer addresses, abstracting away complexities of the underlying implementation.
	        \item Enhanced connection stability by integrating multi-threading for heartbeat monitoring, facilitating automatic re-establishment of SSL connections as required for continuous operation.
	        \item Boosted efficiency and throughput by employing a multi-threaded approach to queue and send packets, optimizing network performance and data handling.
        \end{itemize}
	\item Enabled fault diagnosis \& system reliability with \textbf{C++} library that created files detailing recent activity from failed \textbf{Docker}/\textbf{Kubernetes} containers, enabling more precise troubleshooting and system insights.
        \begin{itemize}
	        \item Optimized log management using circular buffers for priority-based storage, implemented \textbf{multi-threading}, and established \textbf{IPC}-based communication to coordinate across multiple containers.
        \end{itemize}
	\item Enhanced alerting and monitoring by developing data publishing microservice that streamed critical data from containers leveraging \textbf{gRPC} for transmission, \textbf{Fluent Bit} for filtering and enrichment, \textbf{Kafka} for publication.
        \begin{itemize}
	        \item Improved communication efficiency by developing a \textbf{C++} client library with auto-generated \textbf{gRPC} sources, simplifying client initialization, request creation, and stub method invocations.
	        \item Optimized data processing workflows using \textbf{Fluent Bit} for advanced filtering/enrichment, leading to efficient, content-based routing and improved data stream management with Stream Processor.
        \end{itemize}
	\item Significantly reduced application suite build/test times by \textbf{>3 hours} through proposing, planning, and leading an intern project focused on process optimization and efficiency in a containerized build environment.
        \begin{itemize}
	        \item Dramatically reduced the number of files compiled by implementing modern \textbf{CMake} practices, resulting in a significant improvement in build efficiency and a more streamlined development workflow.
	        \item Accelerated development by implementing ccache in \textbf{Docker} build environment, cutting down data transfer with \textbf{volume mounts} to the host, resulting in over 95\% faster build times on Apple chips.
	        \item Optimized efficiency by integrating external libraries into \textbf{Docker} images, drastically reducing download and build times, while also simplifying the process of configuring and managing different library versions.
	        \item Effectively managed and mentored participants, providing guidance through the project's technical and operational complexities, ensuring successful project completion and a valuable learning experiences.
        \end{itemize}
	\item Boosted team velocity by 25\% over three-year tenure as a \textbf{Scrum Master} for 8-member development team, all while excelling in my primary role as a developer.
        \begin{itemize}
	        \item Successfully drove project outcomes by streamlining project workflows, efficiently managing tasks in \textbf{JIRA}, facilitating productive meetings, and fostering collaboration with leaders across various teams.
        \end{itemize}
	\item Accelerated code review completions and development quality by revitalizing processes and training, fostering clear communication, faster issue resolution, and increased team knowledge.
        \begin{itemize}
	        \item Expedited merges by broadening reviewer pool with a template that captured crucial details, increasing contributions from all skill levels, boosting team knowledge and preserving a valuable historical record.
	        \item Enhanced quality of collaborative development resulting in improved code quality, faster issue resolution by delivering code review training that emphasized effective communication and thorough feedback.
        \end{itemize}
	\item Lowered dependency on individual expertise by initiating peer education program, conducting needs assessments, mobilizing subject matter experts, and creating a comprehensive video knowledge base.
        \begin{itemize}
	        \item Boosted technical proficiency of junior developers by holding regular skill-up sessions resulting in a knowledge base populated with \textbf{C4}, \textbf{Sequence}, and \textbf{State} Diagrams.
        \end{itemize}
	\item \textbf{Deployed}, debugged and administered \textbf{Linux-based VMs} using \textbf{Jenkins} to develop, test, and deploy \textbf{Docker}/\textbf{Kubernetes} containers.
	\item Ensured rapid issue resolution and system reliability through critical \textbf{on-call technical support}, demonstrating a deep understanding of system architecture and cross-team product integration.
	\item Streamlined artifact synchronization between legacy \textbf{Perforce} and host build system using dedicated \textbf{Docker} container. Implemented \textbf{Bash} scripting and \textbf{volume mount}s for efficient file transfer.
	\item Eliminated \textbf{cybersecurity} risks by monitoring vulnerabilitites using \textbf{Blackduck} and \textbf{Security Scorecard}, \textbf{JIRA} tracking of resolution, leading to a perfect security assessment for the project.
	\item Mastered complex \textbf{regular expressions} for file identification by name and content with tools such as \textbf{find}, \textbf{ripgrep}, and \textbf{ag}, applied techniques for mass text editing in \textbf{Vim} and \textbf{Obsidian}.
	\item Deep intellectual curiosity and passion about learning through \textbf{methodical study}, \textbf{organized note-taking} using \textbf{Zettelkasten} method, systematic reviews using \textbf{spaced repetition flashcards}.
\end{itemize}

\vspace{-1mm}
\textbf{Viasat} \hfill San Diego, CA\\
\textit{Software Engineer Intern} \hfill June 2017 - August 2017\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Collaborated with an interdisciplinary team to consolidate multiple hardware testing tools into a single server rack, automating modem testing processes.
    \item Created equipment tests using \textbf{C++}, automated tests and reporting of results using \textbf{Python}, ensuring seamless communication and compatibility between devices.
    \item Performed extensive debugging and optimization of the automated system, ensuring robust performance in diverse operational conditions.
\end{itemize}

\textbf{United States Navy} \hfill \\
\textit{Information Systems Technician} \hfill 2007 - 2012\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Obtained \textbf{TS/SCI/NSA Security Clearance}, demonstrating a commitment to stringent security protocols and a proven track record of trustworthiness and reliability in handling classified information.
	\item Configured, maintained, and monitored ship-wide \textbf{local-area network} including \textbf{servers}, \textbf{firewalls}, \textbf{routers}, and \textbf{switches}.
	\item \textbf{Supervised} five-member team of diverse backgrounds and life experiences through daily operations by focusing on respect, communication, and motivation.
\end{itemize}

\header{Skills}
Artifactory, Bash, C++, CMake, Cap'n Proto, Confd, Consul, Docker, Docker-compose, Fluent bit, GDB, Google Test, Graphana, gRPC, Helm, JIRA, Jenkins, Kubernetes, OpenSSL, Python, Redis, Splunk, Terraform, Valgrind, Vault
\\
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{University of California San Diego}\hfill \\
BS in Computer Science \hfill \\
\begin{itemize} \itemsep 1pt
	\item Organizations: \textbf{Vice President} of Student Veterans Organization where I advocated for student veterans and organized events including Raytheon Resume Panel \& Networking Event, and Amazon Alexa Hackathon.
\end{itemize}
\vspace{2mm}

%==== Certificate ====%
\header{Certificates}
\begin{itemize} \itemsep 1pt
	\item C++ Certified Entry-Level Programmer, C++ Institute - 2024
\end{itemize}
\vspace{2mm}

\end{document}
